%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks = True]{hyperref}

\name{Zeren Tan} % Your name
\address{\textbf{Email:} {\color{blue} thutzr1019@gmail.com} \makebox[12em]{}\textbf{Phone:} (+86)~188~$\cdot$~0550~$\cdot$~0687~}

\address{\textbf{Address:} \#3 Zijing Student Apartment, Tsinghua University \\ Beijing, PR 100084, China}



\address{}

\address{\textbf{Homepage:} \href{https://thutzr.github.io}{Zeren Tan}}
 % Your address

 % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Tsinghua University} \hfill {Aug. 2016 - Present} \\ 
B.S. in Civil Engineering \\
Minor in Mathematics
% \smallskip \\
%\textbf{Rank:} 8/69
\end{rSection}

\begin{rSection}{Courses}
\begin{itemize}
    \item \textbf{Major}: 
    Calculus A (1): A+ (100), Calculus A (2): A+ (100), Operations Research: A (95+), Probability and Statistics: A, Linear Algebra: A- (90+), Physics for Scientists and Engineers: A, Structural Mechanics: A, Fundamental of Elasticity and Finite Element Method: A, Student Research Training: A
    \item \textbf{Minor}:
    Ordinary Differential Equation and Dynamic Systems, Abstract Algebra, Differential Geometry, Complex Analysis
    \item \textbf{Coursera}:
    Series courses of deeplearning.ai; Divide and Conquer, Sorting and Searching, and Randomized Algorithms; Graph Search, Shortest Paths, and Data Structures
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Tsinghua University}{Dec. 2017 - Present}{A Dynamic Model for Traffic Flow Prediction Using Updated DRN}{Professor Ruimin Li}
\item We proposed an updated DRN model based on original DRN.
\item We processed 100,000+ of traffic flow data from different sensors using Deep Learning Algorithm.
\item Our results on 14 traffic flow detectors showed that our model outperforms LSTM and DRN.
\item First-authored paper is going to be submitted.
\end{rSubsection}

\begin{rSubsection}{Tsinghua University}{Mar. 2018 - Present}{Traffic Incidents Duration Prediction Based On Deep Survival Analysis}{Professor Ruimin Li}
\item We introduced a deep learning model called Deep Survival into traiffc incidents duration prediction.
\item We processed 100,000+ of traffic incidents data from different areas using survival analysis method.
\item Our results showed that deep survival analysis model is well-suited in predicting traffic incidents duration and outperforms some state-of-the-art models.
\item Second-authored paper is being written.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Purdue University}{Aug. 2018 - Sep. 2018}{High-capacity Dynamic Traffic Assignment Algorithms}{Professor Satish Ukkusuri}
\item We proposed a polynomial graph-based algorithm that can be used in cases where optimal solution is not required.
\item We propsed an exact algorithm for dynamic ride-sharing problems including requests integrating and trip-vehicle matching and computed its running time which is $O(1.2312^{|\mathcal{E}|})$, where $\mathcal{E}$ is the number of edges in the graph.
\item First-authored paper is being written.
\end{rSubsection}

\begin{rSubsection}{Tsinghua University}{Jan. 2019 - Present}{Addressing the Minimum Automobiles Fleeting Problem}{Professor Ruimin Li}
\item We are going to address the problem of how many automobiles an urban city need in the future to serve all trip requests. The major work is to design algorithms for ride-sharing, vehicle routing, dynamic traffic assignment, network reduction and related problems. As well as exact or heuristic algorithms, we are going to give online algorithms so that they can be applied in actual mobile platforms.
\end{rSubsection}
%------------------------------------------------

\end{rSection}

\begin{rSection}{Fellowship}
\begin{itemize}
\item Tsinghua Spark Talent Program Fellowship (since 2018)
	\begin{itemize}
		\item 46/3600, prestigious college innovation society
		\item The only one selected from the Department of Civil Engineering (110 students)
	\end{itemize}
\end{itemize}
\end{rSection}

\begin{rSection}{Scholarships \& Awards}
\begin{itemize}
	\item Award for Excellence in Comprehensive Performance, 2018
	\item Award for Excellence in Scientific and Technological Innovations, 2018
	\item National Encouragment Scholarship, 2018
	\item Jian Luo Scholarship, 2018
	\item Meritorious Winner in Interdisciplinary Contest In Modeling (group leader), 2018
	\item 2nd prize in Tsinghua Mathematical Modeling Contest, 2018
	\item National Encouragment Scholarship, 2017
	\item 1st place in Tsinghua Undergraduate Mathematics Competition (Group of Calculus), 2017
	\item 1st prize in Chinese Undergraduate National Mathematics Competition, 2017
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, Java, MATLAB, C/C++, CPLEX\\
Tools & \LaTeX, Git, Linux, Keras
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
